---
output: html_document
---

Suburbs or city? It’s a first-date type of question.  Yes, it’s that important.  Luckily, both my wife and I have always been amenable to the “burbs”, and while we haven't made the move just yet, it’s certainly on the horizon.  That’s why I was happy to see WalletHub’s [comprehensive study](http://wallethub.com/edu/best-worst-small-cities-to-live-in/16581/) ranking the best and worst small towns in America.  WalletHub looks at 22 metrics and ranks towns on affordability, economic health, education & health and quality of life and gives each town an overall score (check out WalletHub’s full [methodology](https://wallethub.com/edu/best-worst-small-cities-to-live-in/16581/#methodology) ).  

Data on 1,200 towns is cool, but I care mostly about suburbs in the Chicago-land area.  In this analysis I scrape the study’s results, and subset to suburbs within 60 driving miles of downtown Chicago. Only towns with populations between 25,000 and 100,000 residents were included in WalletHub’s study.  Unfortunately, that excludes larger suburbs (like Naperville) and smaller suburbs (like Western Springs) from the analysis.

<br>

<center> <h4>Suburbs Near Chicago (Interactive Table)</h4> </center>

```{r setOptions, message=FALSE,echo=F}
library(googleVis)
op <- options(gvis.plot.tag='chart')
```

```{r ComboExample, results='asis', tidy=FALSE, echo=FALSE}
load("PLOTS/tablePlot")

plot(townTable)
```

<br>

<h3>The Trade Off</h3>

I also wanted to compare a suburb’s overall score with its distance from downtown Chicago.  In general, I have a preference toward being closer to Chicago.  Even if you live in the burbs, you’ll likely commute into the city for work or visit frequently for social engagements. 

Below you can see how the different suburbs match up against each on score and distance from Chicago. I’ve also included some clustering.  For example, the blue points represent suburbs that have an above average score, but are also further away than the average distance from Chicago. 


<br>

<center> <h4>Overall Scores Vs. Distance from Downtown Chicago (Interactive Scatterplot)</h4> </center>

```{r set-options, echo=FALSE, cache=FALSE}
options(RCHART_WIDTH = 1000, RCHART_HEIGHT = 400)
```

```{r, echo=FALSE, cache=F, results='asis', comment=NA}
load("PLOTS/scatterPlot")

scatterPlot$print('chart1', include_assets=T)

```

If you are looking for a great suburb that isn't too far from the city, a good place to start would be with towns like Northbrook, Wilmette, Tinley Park, Glenview and Orland Park, to name a few. 

*You can find the code for this analysis on my [github profile](https://github.com/mannybernabe/smallTownRank_Final).*



